### 2021-11-08 manuscript.Rmd
removed redundant figures

## *Median Bias in Empirical Effect Size Estimates*   
\noindent
```{r, fig.heigth = 4.72, fig.width = 6}
knitr::include_graphics("figures/figure7b.tiff", dpi = 300)
```

@@

## Figure 8
## *Bias-Variance in Empirical Effect Size Estimates*  
\noindent
```{r, fig.heigth = 4.72, fig.width = 7}
knitr::include_graphics("figures/figure8b.tiff", dpi = 300)
```

@@

## Figure A1 
## *Distribution of Effect Sizes Using Fixed versus Independent Segments Hypothesis Testing*
\noindent
```{r, fig.heigth = 20}
knitr::include_graphics("appendix/figures/figureA1.tiff", dpi = 1200)
```

>>>>

## *Median Bias in Empirical Effect Size Estimates*   
\noindent
```{r, fig.heigth = 4.72, fig.width = 6}
knitr::include_graphics("figures/figure7.tiff", dpi = 300)
```

@@

## Figure 8
## *Bias-Variance in Empirical Effect Size Estimates*  
\noindent
```{r, fig.heigth = 4.72, fig.width = 7}
knitr::include_graphics("figures/figure8.tiff", dpi = 300)
```

@@

## Figure A1 
## *Distribution of Effect Sizes Using Fixed versus Independent Segments Hypothesis Testing*
\noindent
```{r, fig.heigth = 20}
knitr::include_graphics("appendix/figures/figureA1.tiff", dpi = 300)
```
